Bird beak's elaboration and exploration: data preparation

### 2022-06-30 Analysis/01-Data_preparation.Rmd
removed NAs

@@

## Fill in the level1
for(clade in 1:length(clade_info_passerines$passerine_big_clades)) {
  clade_name <- names(clade_info_passerines$passerine_big_clades)[clade]
  shapespace_passeriformes[clade_info_passerines$passerine_big_clades[[clade]], "level1"] <- clade_name
}
## Fill in the level2
for(clade in 1:length(clade_info_passerines$passerine_small_clades)) {
  clade_name <- names(clade_info_passerines$passerine_small_clades)[clade]
  shapespace_passeriformes[clade_info_passerines$passerine_small_clades[[clade]], "level2"] <- clade_name
}
shapespace_passeriformes[, "level1"] <- as.factor(shapespace_passeriformes[, "level1"])
shapespace_passeriformes[, "level2"] <- as.factor(shapespace_passeriformes[, "level2"])

>>>>

## Check what's happening with Neodrepanis_hypoxantha

@@

## Fill in the level1
for(clade in 1:length(clade_info_passerines$passerine_big_clades)) {
  ## Get the clade name
  clade_name <- names(clade_info_passerines$passerine_big_clades)[clade]
  ## Attribute the species/clade
  shapespace_passeriformes[clade_info_passerines$passerine_big_clades[[clade]], "level1"] <- clade_name
  ## Remove species not present originally in the shapespace
  if(length(nas <- which(apply(shapespace_passeriformes[, 1:8], 1, function(row) any(is.na(row))))) > 0) {
      shapespace_passeriformes <- shapespace_passeriformes[-nas, ]
  }
}
## Fill in the level2
for(clade in 1:length(clade_info_passerines$passerine_small_clades)) {
  ## Get the clade name
  clade_name <- names(clade_info_passerines$passerine_small_clades)[clade]
  ## Attribute the species/clade
  shapespace_passeriformes[clade_info_passerines$passerine_small_clades[[clade]], "level2"] <- clade_name
  ## Remove species not present originally in the shapespace
  if(length(nas <- which(apply(shapespace_passeriformes[, 1:8], 1, function(row) any(is.na(row))))) > 0) {
      shapespace_passeriformes <- shapespace_passeriformes[-nas, ]
  }
}
shapespace_passeriformes[, "level1"] <- as.factor(shapespace_passeriformes[, "level1"])
shapespace_passeriformes[, "level2"] <- as.factor(shapespace_passeriformes[, "level2"])
